12th International Satisfiability Modulo Theories Competition (SMT-COMP 2017): Rules and Procedures

### 2018-04-05 rules/rules18.tex
Add draft of 2018 rules
Unsat-core Track rules

SMT-COMP entrants must be submitted via StarExec (solvers) \emph{and}
the above web form (accompanying information) until the end of {\bf
  June~4, 2017} anywhere on earth.  After this date no new entrants
will be accepted.  However, updates to existing entrants on StarExec
will be accepted until the end of {\bf June~18, 2017} anywhere on
earth.

@@

In order to perform this unsatisfiability check, the organizers will
use a selection of SMT solvers that have been sound (i.e., not
produced any erroneous result) in the corresponding division of the
main track.  The unsatisfiability of a produced unsatisfiable core is
refuted if the number of checking solvers whose result is \texttt{sat}
exceeds the number of checking solvers whose result is \texttt{unsat},
or if the unsat-core producing solver is used as a checking solver and
its result is \texttt{sat}.  The time limit for checking unsatisfiable
cores is yet to be determined, but is anticipated to be around 5
minutes of wall-clock time per solver.

>>>>

SMT-COMP entrants must be submitted via StarExec (solvers) \emph{and}
the above web form (accompanying information) until the end of {\bf
  June~4, 2017} anywhere on earth.  After this date no new entrants
will be accepted.  However, updates to existing entrants on StarExec
will be accepted until the end of {\bf June~19, 2017} anywhere on
earth.

@@

In order to perform this unsatisfiability check, the organizers will
use a selection of SMT solvers that participate in the main track
of this competition. For each division, the organizers will
use only solvers that have been sound (i.e., not
produced any erroneous result) in test runs of the
main track for this division.
The unsatisfiability of a produced unsatisfiable core is
refuted if the number of checking solvers whose result is \texttt{sat}
exceeds the number of checking solvers whose result is \texttt{unsat}.
The time limit for checking unsatisfiable
cores is yet to be determined, but is anticipated to be around 5
minutes of wall-clock time per solver.
